Matching and merging high-resolution and legacy seismic images

### 2019-08-15 thesis/chapter-merge/paper.tex
moving thesis

    In this example, we find the radius of smoothing using the theoretical approach described in the previous chapter, so 

@@

    We first apply a low-cut filter to the legacy data to remove the low frequency information that is simply not present in the high-resolution image. 
    Next, we adjust the non-stationary smoothing radius using the simple iterative algorithm \cite[]{locfreq} that was described in the previous chapter.

>>>>

    In this example, we find the radius of smoothing using the theoretical approach described in Chapter \ref{ch:chapter-locfreq}, so 

@@

    We first apply a low-cut filter to the legacy data to remove the low frequency information that is simply not present in the high-resolution image. 
    Next, we adjust the non-stationary smoothing radius using the simple iterative algorithm \cite[]{locfreq} that was described in Chapter \ref{ch:chapter-locfreq}.
